outline!

### 2016-05-23 paper.tex
paper: adjust org
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

\section{Background}

In this section we highlight the salient components of Ceph, especially its
\emph{object class} feature that offers users the ability to load and execute
application-specific codes. We provide a description of our motivating
example, a high-performance distributed shared-log built upon Ceph that makes
extensive use of the object class facility, and then we present the challenges
that application developers face when using this extensibility feature offered
by the storage system.

@@

\paragraph*{Towards a CORFU Object Interface}
The state-machine diagram in Figure~\ref{fig:corfu-sm} shows the composition of
actions for each component of the CORFU interface. For instance, all operations
begin by applying an \emph{epoch guard} that ensures the request is tagged with
an up-to-date epoch value. The \emph{read} (R) and \emph{write} (W) operations
both proceed by (1) examining metadata associated with the target position, (2)
performing I/O to read or write the log entry, and in the case of a write, (3)
updates metadata for the target log position.

@@

The primary concern of an application developer when implementing an object
interface in Ceph is deciding how native interfaces are composed into a
compound operation. These types of decisions are commonly referred to as
physical design, and can affect performance and application flexibility.  For
instance, one valid design option is to store each log position in an object
with a name using a one-to-one mapping with the log entry position.  This
would simplify the design of the \emph{write} interface because a small amount
of metadata stored as a header in the object could describe the state of the
log entry.  However, as we will see in the next section this choice of a
physical design can result in poor performance compared to other designs.

As we have seen, Ceph provides a rich storage API and places few restrictions
on the structure of applications. So how should we go about implementing CORFU
on Ceph? Our strategy is straightforward: first we will define the entire
design space, and then winnow down this space using a set of targeted
benchmarks. The design space can be divided into three challenges:
selecting a strategy for log entry addressing, choosing a native I/O interface
for storing log entry content, and implementing efficient metadata management.

>>>>

\section{Background and Motivation}

In this section we highlight the salient components of Ceph, especially its
\emph{object class} feature that offers users the ability to load and execute
application-specific codes. We provide a description of our motivating
example, a high-performance distributed shared-log built upon Ceph that makes
extensive use of the object class facility.

@@

As we have seen, Ceph provides a rich storage API and places few restrictions
on the structure of applications. Thus a primary concern when implementing an
object interface in Ceph is deciding how native interfaces are composed into
compound operations in order to implement the semantics of the target
interface. These types of decisions are commonly referred to as
physical design, and can affect performance and application flexibility.
As we will see the design space that developers must operate in is often
large, and its dynamic nature can lead to design decisions that become
obsolete and non-optimal.

@@

To understand the developer process in the context of CORFU we have included the
state-machine diagram in Figure~\ref{fig:corfu-sm} showing the composition of
actions for each component of the CORFU interface which must be mapped onto
Ceph object classes. For instance, all operations begin by applying an
\emph{epoch guard} that ensures the request is tagged with an up-to-date epoch
value. The \emph{read} (R) and \emph{write} (W) operations both proceed by (1)
examining metadata associated with the target position, (2) performing I/O to
read or write the log entry, and in the case of a write, (3) updates metadata
for the target log position.

As an example, one valid design option is to store each log position in an
object with a name using a one-to-one mapping with the log entry position.
This would simplify the design of the \emph{write} interface because a small
amount of metadata stored as a header in the object could describe the state
of the log entry.  However, as we will see this choice of a physical design
can result in poor performance compared to other designs. In the remainder of
this section we will define the entire design space and use a set of targetted
benchmarks to arrive at a final design. Finally we will show that these design
decisions can lead to non-optimal decisions and suggest an automated approach
is desirable.

\subsection{Challenges}

The design space can be divided into three challenges: selecting a strategy
for log entry addressing, choosing a native I/O interface for storing log
entry content, and implementing efficient metadata management.
